### 2019-11-25 paper/results.tex
Uncertanties added to Table 9 and Future work shortened

Table~\ref{tab:six_factor} summarizes the six factor for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, six factor is calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for the $^{233}$U and TRU cases but 
considerably declines for the Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factor for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
			material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Table~\ref{tab:six_factor} summarizes the six factor for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, six factor is calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for the $^{233}$U and TRU cases but 
considerably declines for the Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factor for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X | p{0.1\textwidth}} \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c|}{Startup fissile 
			material} & \multirow{3}{*}{$\pm\bar{\sigma}$} \\ 
			\cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c|}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil & \space 
		\\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31&4.9E-4\\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75&2.1E-4 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15&4.6E-4 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81&6.2E-4 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99&1.7E-6 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00&6.5E-11 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
